---
title: bmuniz_resume_pt
author: Bianca Muniz
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles_html.css', 'resume']
    # css: ['css/custom_resume.css', 'css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML" is automatically updated in update_resume.R 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

#load packages
library(glue)

#source helper functions
source('helper_functions.R')

position_data <- read.csv2('./data/position_data_pt2.csv', stringsAsFactors = F)
skill_data <- read.csv('./data/skill_data.csv', stringsAsFactors = F)
```

# Aside

## Contact {#contact}

```{r contactinfo}

# Adjust contact info based on document type - html has link while pdf does not
if(params$doctype == "HTML") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Cajamar, São Paulo
    - <i class="fa fa-phone"></i> <a href="tel:+11972562470">(11) 972562470</a>
    - <i class="fa fa-envelope"></i> bnc.muniz@gmail.com
    - <i class="fa fa-envelope"></i> biancamuniz@apublica.com
    - <i class="fa fa-github"></i> [github.com/biamuniz](https://github.com/biamuniz)
    - <i class="fab fa-linkedin-in"></i> [linkedin.com/bmuniz](https://www.linkedin.com/in/bmuniz/)')
} 

if(params$doctype == "PDF") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Cajamar, São Paulo
    - <i class="fa fa-phone"></i> <a href="tel:+11972562470">(11) 972562470</a>
    - <i class="fa fa-envelope"></i> bnc.muniz@gmail.com
    - <i class="fa fa-envelope"></i> biancamuniz@apublica.com
    - <i class="fa fa-github"></i> [github.com/biamuniz](https://github.com/biamuniz)
    - <i class="fab fa-linkedin-in"></i> [linkedin.com/bmuniz](https://www.linkedin.com/in/bmuniz/)')
}

```

```{r download}
# if doctype is html add link to download a pdf version
if(params$doctype == "HTML"){
  cat("[<i class='fas fa-download'></i> Download as a PDF](https://github.com/biamuniz/resume/raw/main/bianca_muniz_resume.pdf)")
}

```

<br>

## Tech skills {#skills}

```{r codingskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Tech")

```

## R skills {#rpackages}

```{r rskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "R Packages")

```


## Languages

-   Portuguese
-   English
-   Spanish

## Disclaimer {#disclaimer}

```{r}

# set disclaimer in bottom right corner based on doctype
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/biamuniz/resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/biamuniz/resume** 
  ")
}
```

Last updated on `r Sys.Date()`. <br> <br>

# Main

## Bianca Muniz {#title}

I enjoy working with data to find and deliver insights, solve business problems, and build tools that help people work more efficiently. I moved into data science after 10+ years working in public policy and public relations.

## Professional Experience {data-icon="suitcase"}

```{r jobs}
print_section(position_data, 'work')
```

## Education {data-icon="graduation-cap" data-concise="true"}

```{r education}
print_section(position_data, 'education')
```

## Awards {data-icon="award" data-concise="true"}

```{r awards}
print_section(position_data, 'awards')
```

## Talks {data-icon="award" data-concise="true"}

```{r talks}
print_section(position_data, 'talks')
```

## Trabalho Voluntário

-   R-Ladies São Paulo
-   Cursinho pré-vestibular Jeannine Aboulafia


## Disclaimer {#disclaimer}

```{r}

# set disclaimer in bottom right corner based on doctype
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/biamuniz/resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/biamuniz/resume** 
  ")
}
```

Last updated on `r Sys.Date()`. <br> <br>
